MS_CNuptake.Rmd

### 2023-05-25 MS_CNuptake.Rmd
solve the issue for mass balance

## Combine forest and grassland global fields
```{r}
#combine into 2 pfts
npp_pft <- available_grid2* (npp_f*forest_percent +npp_g*grass_percent)
npp_forest <- available_grid2* (npp_f*forest_percent)
npp_grass <- available_grid2* (npp_g*grass_percent)

@@

#final nue - calculated from final results
#forest nue:
(55.74/0.61) 
#grassland nue:
(16.36/0.34)
#total nue:
76.00 # as shown in figure
#forest nue uncertainty:
(55.74/0.61)  * sqrt( (10.62/55.74)^2 +(0.22/0.61)^2)
#grassland nue uncertainty:
(16.36/0.34) * sqrt( (9.72/16.36)^2 +(0.15/0.34)^2)
#pft
(72.10/0.95) * sqrt( (14.40/72.10)^2 +(0.26/0.95)^2)
```

>>>>

## Combine forest and grassland global fields
```{r}
#combine into 2 pfts
npp_pft <- available_grid2* (npp_f*forest_percent +npp_g*grass_percent)
#define an available available_grid3 - that includes NA information of npp_f and npp_g:
#for npp_f and npp_g, we transfer those negative values (<0) to NA. we need to know and specify all these NA grids, and use it through calculations
#this is important, as it will make balance for weighted-sum calculations (i.e. all components in forest and grassland have the same NA grids).

available_grid3 <- npp_pft
available_grid3[is.na(available_grid3)==F] <- 1
#combine available_grid3 and available_grid2
available_grid2 <- available_grid3*available_grid2

npp_forest <- available_grid2* (npp_f*forest_percent)
npp_grass <- available_grid2* (npp_g*grass_percent)

@@

#final nue - calculated from final results
#forest nue:
(55.70/0.61) 
#grassland nue:
(16.40/0.34)
#total nue:
76.00 # as shown in figure
#forest nue uncertainty:
(55.70/0.61)  * sqrt( (10.58/55.70)^2 +(0.22/0.61)^2)
#grassland nue uncertainty:
(16.40/0.34) * sqrt( (9.42/16.40)^2 +(0.14/0.34)^2)
#pft
(72.10/0.95) * sqrt( (14.17/72.10)^2 +(0.26/0.95)^2)
```
